\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1.8cm]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{subcaption}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage{enumitem}
\pgfplotsset{compat=1.18}

\definecolor{bridge}{HTML}{2F6B9A}
\definecolor{forward}{HTML}{2E8B57}
\definecolor{direct}{HTML}{C96C2C}
\definecolor{accent}{HTML}{44546A}
\definecolor{panel}{HTML}{F4F7FA}
\definecolor{gridline}{HTML}{D8DEE8}
\definecolor{increasecolor}{HTML}{A64B2A}
\definecolor{decreasecolor}{HTML}{1F7A66}

\newcommand{\increase}[1]{\textcolor{increasecolor}{#1}}
\newcommand{\decrease}[1]{\textcolor{decreasecolor}{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\statbox}[2]{%
  \begin{tcolorbox}[colback=panel,colframe=accent,boxrule=0.4pt,arc=1mm,left=1mm,right=1mm,top=1mm,bottom=1mm]
  \centering{\Large\bfseries #1}\\[-1mm]{\scriptsize #2}
  \end{tcolorbox}%
}

\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=bridge,
  pdftitle={Sigrok BMS Protocol Decoder Capture Analysis},
}

\title{Sigrok BMS Protocol Decoder Capture Analysis}
\author{Generated from offline sigrok/PulseView analysis outputs}
\date{}

\begin{document}
\maketitle

\section*{Executive Summary}

\begin{tabularx}{\textwidth}{YYYY}
\statbox{30}{total captures} &
\statbox{17}{RS485/UART captures} &
\statbox{13}{CAN captures} &
\statbox{19 / 6 / 5}{Bridge / Forward / Direct} \\
\end{tabularx}

\begin{tcolorbox}[colback=panel,colframe=accent,title=Key observations]
\begin{itemize}[leftmargin=*]
\item Anenji Pylon RS485 JKBMS shows the clearest RS485 latency change: Direct cable is -4.58 ms (-47.2\%) versus Bridge for average request-to-response latency.
\item Growatt RS485 JKBMS has slower worst-case exchange timing: Direct cable is +21.48 ms (+40.1\%) versus Bridge for full-exchange P95 latency.
\item Growatt CAN SeplosBMS cycles are shorter in Direct cable mode: Direct cable is -164.25 ms (-19.3\%) versus Bridge for average CAN cycle duration.
\item Growatt CAN JKBMS frame rate stays effectively flat across modes: Direct cable is +0.1 frames/s (+0.2\%) versus Bridge.
\end{itemize}
\end{tcolorbox}


\begin{landscape}
\section*{Capture Context Metadata}

\small
This table separates the decoded bus from the physical devices used during the
test. Inverter protocol values may come from the captured bus or from fixed
test metadata for inverter models with a single tested protocol. \texttt{not
captured} means the opposite-side protocol is not proven by that capture or by
test metadata; it is not inferred from the comparison group name.

\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\setlength{\LTpre}{0.45em}
\setlength{\LTpost}{0.65em}
\begin{longtable}{@{}L{1.6cm}L{3.6cm}L{2.2cm}L{3.0cm}L{2.0cm}L{2.8cm}L{2.0cm}L{3.0cm}@{}}
\caption{Capture context metadata.}\\
\toprule
Mode & Capture & Captured side & Captured protocol & Inverter device & Inverter protocol & BMS device & BMS protocol \\
\midrule
\endfirsthead
\caption[]{Capture context metadata, continued.}\\
\toprule
Mode & Capture & Captured side & Captured protocol & Inverter device & Inverter protocol & BMS device & BMS protocol \\
\midrule
\endhead
Bridge & bridge/china-tower-modbus-rs485 & BMS side & China Tower Modbus RS485 & Growatt & Pylon CAN & JKBMS & China Tower Modbus RS485 \\
Bridge & bridge/easun-daly-rs485 & BMS side & Daly RS485 & Easun & Pylon CAN & Daly BMS & Daly RS485 \\
Bridge & bridge/growatt-rs485 & Inverter side & Growatt RS485 & Growatt & Growatt RS485 & JKBMS & not captured \\
Bridge & bridge/growatt-seplos-rs485 & Inverter side & Growatt RS485 & Growatt & Growatt RS485 & SeplosBMS & not captured \\
Direct cable & direct/growatt-rs485 & Shared bus & Growatt RS485 & Growatt & Growatt RS485 & JKBMS & Growatt RS485 \\
Bridge Forward & bridge\_forward/growatt-rs485 & Shared bus & Growatt RS485 & Growatt & Growatt RS485 & JKBMS & Growatt RS485 \\
Bridge Forward & bridge\_forward/growatt-seplos-rs485 & Shared bus & Growatt RS485 & Growatt & Growatt RS485 & SeplosBMS & Growatt RS485 \\
Bridge & bridge/jkbms-modbus-rs485 & BMS side & JKBMS Modbus RS485 & Growatt & not captured & JKBMS & JKBMS Modbus RS485 \\
Bridge & bridge/pace-modbus-rs485 & BMS side & PACE Modbus RS485 & Growatt & not captured & JKBMS & PACE Modbus RS485 \\
Bridge & bridge/pylon-rs485 & Inverter side & Pylon RS485 & Growatt & Pylon RS485 & JKBMS & not captured \\
Bridge & bridge/anenji-pylon-rs485 & Inverter side & Pylon RS485 & Anenji & Pylon RS485 & JKBMS & not captured \\
Direct cable & direct/anenji-jkbms-pylon-rs485 & Shared bus & Pylon RS485 & Anenji & Pylon RS485 & JKBMS & Pylon RS485 \\
Direct cable & direct/anenji-seplos-pylon-rs485 & Shared bus & Pylon RS485 & Anenji & Pylon RS485 & SeplosBMS & Pylon RS485 \\
Bridge Forward & bridge\_forward/anenji-pylon-rs485 & Shared bus & Pylon RS485 & Anenji & Pylon RS485 & JKBMS & Pylon RS485 \\
Bridge Forward & bridge\_forward/anenji-seplos-pylon-rs485 & Shared bus & Pylon RS485 & Anenji & Pylon RS485 & SeplosBMS & Pylon RS485 \\
Bridge & bridge/voltronic-modbus-rs485 & BMS side & Voltronic Modbus RS485 & Growatt & Pylon RS485 & SeplosBMS & Voltronic Modbus RS485 \\
Bridge & bridge/wow-modbus-rs485 & BMS side & WOW Modbus RS485 & Growatt & Pylon RS485 & JKBMS & WOW Modbus RS485 \\
Bridge & bridge/deye-can & Inverter side & Deye CAN & Growatt & Deye CAN & JKBMS & not captured \\
Bridge & bridge/goodwe-can & Inverter side & GoodWe CAN & Growatt & GoodWe CAN & SeplosBMS & not captured \\
Bridge & bridge/growatt-can & Inverter side & Growatt CAN & Growatt & Growatt CAN & JKBMS & not captured \\
Bridge & bridge/growatt-seplos-can & Inverter side & Growatt CAN & Growatt & Growatt CAN & SeplosBMS & not captured \\
Direct cable & direct/growatt-can & Shared bus & Growatt CAN & Growatt & Growatt CAN & JKBMS & Growatt CAN \\
Direct cable & direct/growatt-seplos-can & Shared bus & Growatt CAN & Growatt & Growatt CAN & SeplosBMS & Growatt CAN \\
Bridge Forward & bridge\_forward/growatt-can & Shared bus & Growatt CAN & Growatt & Growatt CAN & JKBMS & Growatt CAN \\
Bridge Forward & bridge\_forward/growatt-seplos-can & Shared bus & Growatt CAN & Growatt & Growatt CAN & SeplosBMS & Growatt CAN \\
Bridge & bridge/jkbms-can & BMS side & JKBMS CAN & Growatt & Growatt CAN & JKBMS & JKBMS CAN \\
Bridge & bridge/pylon-can & BMS side & Pylon CAN & Growatt & Growatt CAN & JKBMS & Pylon CAN \\
Bridge & bridge/sma-can & BMS side & SMA CAN & Growatt & Growatt CAN & SeplosBMS & SMA CAN \\
Bridge & bridge/sofar-can & BMS side & Sofar CAN & Growatt & Growatt CAN & SeplosBMS & Sofar CAN \\
Bridge & bridge/victron-can & BMS side & Victron CAN & Growatt & Growatt CAN & SeplosBMS & Victron CAN \\
\bottomrule
\end{longtable}
\endgroup
\end{landscape}



\begin{landscape}
\begingroup
\setlength{\tabcolsep}{3pt}
\setlength{\LTleft}{\fill}
\setlength{\LTright}{\fill}
\setlength{\LTpre}{0.45em}
\setlength{\LTpost}{0.65em}
\small Abbreviations: GW=Growatt, JK=JKBMS, Sep=SeplosBMS, Anj=Anenji, Py=Pylon, IC=inter-cycle.

\begin{longtable}{@{}L{1.6cm}L{2.2cm}L{1.5cm}L{2.2cm}L{5.0cm}L{1.4cm}L{1.4cm}L{3.7cm}@{}}
\caption{Direct cable versus Bridge values, sorted by absolute percentage difference.}\\
\toprule
Inv. dev. & Inv. proto. & BMS dev. & BMS proto. & Metric & Direct & Bridge & Diff \\
\midrule
\endfirsthead
\caption[]{Direct cable versus Bridge values, continued.}\\
\toprule
Inv. dev. & Inv. proto. & BMS dev. & BMS proto. & Metric & Direct & Bridge & Diff \\
\midrule
\endhead
GW & GW CAN & JK & GW CAN & Cycles/s & 0.2 & 0.1 & \increase{+0.1 (+100\%)} \\
GW & GW CAN & JK & GW CAN & Cycle min (ms) & 4980.23 & 9980.7 & \decrease{-5000.47 (-50.1\%)} \\
GW & GW CAN & JK & GW CAN & Cycle avg (ms) & 4980.23 & 9980.7 & \decrease{-5000.47 (-50.1\%)} \\
GW & GW CAN & JK & GW CAN & Cycle max (ms) & 4980.23 & 9980.7 & \decrease{-5000.47 (-50.1\%)} \\
GW & GW CAN & JK & GW CAN & Cycle P95 (ms) & 4980.23 & 9980.7 & \decrease{-5000.47 (-50.1\%)} \\
GW & GW CAN & Sep & GW CAN & Cycle min (ms) & 129.93 & 251.23 & \decrease{-121.3 (-48.3\%)} \\
Anj & Py 485 & JK & Py 485 & Req->Rsp avg (ms) & 5.12 & 9.71 & \decrease{-4.58 (-47.2\%)} \\
GW & GW CAN & Sep & GW CAN & IC gap min (ms) & 168.23 & 114.67 & \increase{+53.56 (+46.7\%)} \\
GW & GW CAN & Sep & GW CAN & Cycle max (ms) & 831.77 & 1496.22 & \decrease{-664.45 (-44.4\%)} \\
Anj & Py 485 & JK & Py 485 & Req->Rsp P95 (ms) & 5.69 & 9.91 & \decrease{-4.22 (-42.6\%)} \\
GW & GW 485 & JK & GW 485 & Full exchange P95 (ms) & 75 & 53.52 & \increase{+21.48 (+40.1\%)} \\
GW & GW CAN & Sep & GW CAN & Cycle P95 (ms) & 831.77 & 1221.32 & \decrease{-389.55 (-31.9\%)} \\
GW & GW 485 & JK & GW 485 & Full exchange avg (ms) & 59.34 & 49.09 & \increase{+10.24 (+20.9\%)} \\
GW & GW 485 & JK & GW 485 & Complete exchanges/s & 2 & 2.5 & \decrease{-0.5 (-20\%)} \\
GW & GW CAN & Sep & GW CAN & Cycles/s & 1.2 & 1 & \increase{+0.2 (+20\%)} \\
GW & GW CAN & Sep & GW CAN & Cycle avg (ms) & 687.13 & 851.37 & \decrease{-164.25 (-19.3\%)} \\
GW & GW CAN & Sep & GW CAN & IC gap avg (ms) & 168.23 & 155.49 & \increase{+12.74 (+8.2\%)} \\
GW & GW 485 & JK & GW 485 & Req->Rsp avg (ms) & 5.13 & 4.76 & \increase{+0.37 (+7.7\%)} \\
Anj & Py 485 & JK & Py 485 & Full exchange avg (ms) & 102.92 & 111.16 & \decrease{-8.25 (-7.4\%)} \\
Anj & Py 485 & JK & Py 485 & Full exchange P95 (ms) & 145.15 & 153.03 & \decrease{-7.88 (-5.1\%)} \\
GW & GW 485 & JK & GW 485 & Req->Rsp P95 (ms) & 5.44 & 5.29 & \increase{+0.14 (+2.7\%)} \\
GW & GW CAN & Sep & GW CAN & IC gap max (ms) & 168.23 & 165.78 & \increase{+2.45 (+1.5\%)} \\
GW & GW CAN & Sep & GW CAN & IC gap P95 (ms) & 168.23 & 165.78 & \increase{+2.45 (+1.5\%)} \\
GW & GW CAN & JK & GW CAN & Frames/s & 52 & 51.9 & \increase{+0.1 (+0.2\%)} \\
Anj & Py 485 & JK & Py 485 & Complete exchanges/s & 0.8 & 0.8 & 0 (0\%) \\
GW & GW CAN & Sep & GW CAN & Frames/s & 13 & 13 & 0 (0\%) \\
\bottomrule
\end{longtable}
\endgroup
\end{landscape}


\section{Protocol Overview Charts}

These charts include every protocol group available in the overview CSV. Missing
topology modes are intentionally left blank, so a group can have one, two, or three
bars depending on the captures currently available.

For RS485/UART charts, the timing terms are:

\begin{itemize}[leftmargin=*]
\item Request-to-response latency: response start minus request end for a
complete paired exchange.
\item Full exchange duration: response end minus request start for a complete
paired exchange. This includes request transmission, turnaround/processing gap,
and response transmission.
\item Inter-exchange gap: response end of one complete exchange to request start
of the next complete exchange.
\item 95th percentile: the value below which 95\% of the measured complete
request/response pairs fall.
\end{itemize}

For CAN charts, cycle duration is the time from the first frame in a detected
CAN burst to the last frame in that burst. CAN cycle duration charts use a
logarithmic y-axis because values span multiple orders of magnitude, from
sub-millisecond single-frame cycles to multi-second capture-length cycles. CAN
cycle P95 is the closest counterpart to RS485/UART full-exchange P95 in this
report.


\begin{figure}[p]
\centering

\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Request-to-response avg (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,5.015) [5.0] (2,14.459) [14.5] (3,4.760) [4.8] (4,49.517) [49.5] (5,4.904) [4.9] (6,4.988) [5.0] (7,4.817) [4.8] (8,9.707) [9.7] (10,99.797) [99.8] (11,4.799) [4.8]};
\addplot+[fill=forward, draw=forward] coordinates {(3,5.008) [5.0] (4,49.604) [49.6] (8,5.489) [5.5] (9,9.470) [9.5]};
\addplot+[fill=direct, draw=direct] coordinates {(3,5.127) [5.1] (8,5.125) [5.1] (9,9.887) [9.9]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Average request-to-response latency for all available RS485/UART protocol groups.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Full exchange 95th percentile (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,53.526) [53.5] (2,297.647) [297.6] (3,53.520) [53.5] (4,97.806) [97.8] (5,13.116) [13.1] (6,66.065) [66.1] (7,148.668) [148.7] (8,153.034) [153.0] (10,119.962) [120.0] (11,65.809) [65.8]};
\addplot+[fill=forward, draw=forward] coordinates {(3,53.485) [53.5] (4,97.846) [97.8] (8,149.320) [149.3] (9,153.002) [153.0]};
\addplot+[fill=direct, draw=direct] coordinates {(3,75.001) [75.0] (8,145.155) [145.2] (9,151.499) [151.5]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{P95 full-exchange duration for all available RS485/UART protocol groups.}
\end{subfigure}

\caption{RS485/UART protocol overview charts.}
\end{figure}



\begin{figure}[p]
\centering

\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=0.99\textwidth,
    height=5.8cm,
    bar width=7pt,
    ymode=log,
    log basis y=10,
    log origin y=infty,
    ytick={0.1,1,10,100,1000,10000},
    yticklabels={\mbox{10\raisebox{0.55ex}{-1}},\mbox{10\raisebox{0.55ex}{0}},\mbox{10\raisebox{0.55ex}{1}},\mbox{10\raisebox{0.55ex}{2}},\mbox{10\raisebox{0.55ex}{3}},\mbox{10\raisebox{0.55ex}{4}}},
    ymin=0.1,
    ymax=119768,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=9.5,
    enlarge x limits=false,
    ylabel={Cycle avg (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN JKBMS,Growatt CAN SeplosBMS,JKBMS CAN,Pylon CAN,SMA CAN,Sofar CAN,Victron CAN},
    x tick label style={text width=1.3cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,1011.013) [1011.0] (2,2399.973) [2400.0] (3,9980.699) [9980.7] (4,851.374) [851.4] (5,9907.993) [9908.0] (6,1900.011) [1900.0] (7,0.231) [0.2] (8,0.229) [0.2] (9,9960.726) [9960.7]};
\addplot+[fill=forward, draw=forward] coordinates {(3,9980.681) [9980.7] (4,755.942) [755.9]};
\addplot+[fill=direct, draw=direct] coordinates {(3,4980.232) [4980.2] (4,687.126) [687.1]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Average CAN cycle duration, log scale.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=0.99\textwidth,
    height=5.8cm,
    bar width=7pt,
    ymode=log,
    log basis y=10,
    log origin y=infty,
    ytick={0.1,1,10,100,1000,10000},
    yticklabels={\mbox{10\raisebox{0.55ex}{-1}},\mbox{10\raisebox{0.55ex}{0}},\mbox{10\raisebox{0.55ex}{1}},\mbox{10\raisebox{0.55ex}{2}},\mbox{10\raisebox{0.55ex}{3}},\mbox{10\raisebox{0.55ex}{4}}},
    ymin=0.1,
    ymax=119768,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=9.5,
    enlarge x limits=false,
    ylabel={Cycle P95 (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN JKBMS,Growatt CAN SeplosBMS,JKBMS CAN,Pylon CAN,SMA CAN,Sofar CAN,Victron CAN},
    x tick label style={text width=1.3cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,1599.871) [1599.9] (2,6275.024) [6275.0] (3,9980.699) [9980.7] (4,1221.318) [1221.3] (5,9907.993) [9908.0] (6,2299.945) [2299.9] (7,0.237) [0.2] (8,0.237) [0.2] (9,9960.726) [9960.7]};
\addplot+[fill=forward, draw=forward] coordinates {(3,9980.681) [9980.7] (4,861.952) [862.0]};
\addplot+[fill=direct, draw=direct] coordinates {(3,4980.232) [4980.2] (4,831.769) [831.8]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{95th-percentile CAN cycle duration, log scale.}
\end{subfigure}

\caption{CAN protocol overview charts.}
\end{figure}



\begin{figure}[p]
\centering

\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Gap min (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,196.256) [196.3] (2,269.414) [269.4] (3,349.429) [349.4] (4,309.189) [309.2] (5,245.181) [245.2] (6,183.842) [183.8] (7,1959.025) [1959.0] (8,647.998) [648.0] (10,130.076) [130.1] (11,189.372) [189.4]};
\addplot+[fill=forward, draw=forward] coordinates {(3,349.433) [349.4] (4,310.158) [310.2] (8,734.886) [734.9] (9,646.656) [646.7]};
\addplot+[fill=direct, draw=direct] coordinates {(3,424.874) [424.9] (8,738.413) [738.4] (9,650.604) [650.6]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Minimum gap between complete RS485/UART exchanges.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Gap avg (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,210.162) [210.2] (2,271.066) [271.1] (3,353.400) [353.4] (4,319.015) [319.0] (5,245.979) [246.0] (6,194.824) [194.8] (7,2693.760) [2693.8] (8,1059.939) [1059.9] (10,139.569) [139.6] (11,199.957) [200.0]};
\addplot+[fill=forward, draw=forward] coordinates {(3,353.211) [353.2] (4,320.460) [320.5] (8,1059.074) [1059.1] (9,1072.162) [1072.2]};
\addplot+[fill=direct, draw=direct] coordinates {(3,440.574) [440.6] (8,1097.088) [1097.1] (9,1106.893) [1106.9]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Average gap between complete RS485/UART exchanges.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Gap max (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,233.716) [233.7] (2,272.681) [272.7] (3,360.509) [360.5] (4,339.692) [339.7] (5,247.000) [247.0] (6,213.041) [213.0] (7,4702.110) [4702.1] (8,1527.191) [1527.2] (10,140.472) [140.5] (11,210.403) [210.4]};
\addplot+[fill=forward, draw=forward] coordinates {(3,360.241) [360.2] (4,339.621) [339.6] (8,1491.398) [1491.4] (9,1611.294) [1611.3]};
\addplot+[fill=direct, draw=direct] coordinates {(3,450.343) [450.3] (8,1495.621) [1495.6] (9,1614.699) [1614.7]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Maximum gap between complete RS485/UART exchanges.}
\end{subfigure}

\caption{RS485/UART inter-exchange gap overview charts.}
\end{figure}



\begin{figure}[p]
\centering

\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=6.5,
    enlarge x limits=false,
    ylabel={Gap min (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN SeplosBMS,Pylon CAN,SMA CAN,Sofar CAN},
    x tick label style={text width=1.55cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,100.186) [100.2] (2,100.259) [100.3] (3,114.669) [114.7] (4,100.164) [100.2] (5,165.308) [165.3] (6,124.888) [124.9]};
\addplot+[fill=forward, draw=forward] coordinates {(3,128.175) [128.2]};
\addplot+[fill=direct, draw=direct] coordinates {(3,168.226) [168.2]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Minimum inter-cycle gap for CAN protocol groups with at least two detected cycles.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=6.5,
    enlarge x limits=false,
    ylabel={Gap avg (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN SeplosBMS,Pylon CAN,SMA CAN,Sofar CAN},
    x tick label style={text width=1.55cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,100.194) [100.2] (2,100.265) [100.3] (3,155.493) [155.5] (4,100.172) [100.2] (5,166.405) [166.4] (6,168.954) [169.0]};
\addplot+[fill=forward, draw=forward] coordinates {(3,160.227) [160.2]};
\addplot+[fill=direct, draw=direct] coordinates {(3,168.228) [168.2]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Average inter-cycle gap for CAN protocol groups with at least two detected cycles.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=6.5,
    enlarge x limits=false,
    ylabel={Gap max (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN SeplosBMS,Pylon CAN,SMA CAN,Sofar CAN},
    x tick label style={text width=1.55cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,100.204) [100.2] (2,100.269) [100.3] (3,165.778) [165.8] (4,100.178) [100.2] (5,168.242) [168.2] (6,382.072) [382.1]};
\addplot+[fill=forward, draw=forward] coordinates {(3,165.778) [165.8]};
\addplot+[fill=direct, draw=direct] coordinates {(3,168.230) [168.2]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Maximum inter-cycle gap for CAN protocol groups with at least two detected cycles.}
\end{subfigure}

\caption{CAN inter-cycle gap overview charts.}
\end{figure}



\begin{figure}[p]
\centering

\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Full exchange min (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,25.537) [25.5] (2,291.574) [291.6] (3,42.256) [42.3] (4,64.023) [64.0] (5,6.283) [6.3] (6,46.481) [46.5] (7,53.582) [53.6] (8,69.060) [69.1] (10,117.499) [117.5] (11,46.519) [46.5]};
\addplot+[fill=forward, draw=forward] coordinates {(3,42.171) [42.2] (4,64.375) [64.4] (8,64.878) [64.9] (9,68.932) [68.9]};
\addplot+[fill=direct, draw=direct] coordinates {(3,49.672) [49.7] (8,60.415) [60.4] (9,65.192) [65.2]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Minimum full-exchange duration for all available RS485/UART protocol groups.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.8cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Full exchange max (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,53.654) [53.7] (2,297.682) [297.7] (3,53.555) [53.6] (4,97.823) [97.8] (5,13.269) [13.3] (6,66.222) [66.2] (7,148.836) [148.8] (8,153.046) [153.0] (10,122.961) [123.0] (11,65.825) [65.8]};
\addplot+[fill=forward, draw=forward] coordinates {(3,53.590) [53.6] (4,98.206) [98.2] (8,149.493) [149.5] (9,153.103) [153.1]};
\addplot+[fill=direct, draw=direct] coordinates {(3,75.141) [75.1] (8,145.355) [145.4] (9,151.609) [151.6]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Maximum full-exchange duration for all available RS485/UART protocol groups.}
\end{subfigure}

\caption{RS485/UART full-exchange range overview charts.}
\end{figure}



\begin{figure}[p]
\centering

\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=0.99\textwidth,
    height=5.8cm,
    bar width=7pt,
    ymode=log,
    log basis y=10,
    log origin y=infty,
    ytick={0.1,1,10,100,1000,10000},
    yticklabels={\mbox{10\raisebox{0.55ex}{-1}},\mbox{10\raisebox{0.55ex}{0}},\mbox{10\raisebox{0.55ex}{1}},\mbox{10\raisebox{0.55ex}{2}},\mbox{10\raisebox{0.55ex}{3}},\mbox{10\raisebox{0.55ex}{4}}},
    ymin=0.1,
    ymax=119768,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=9.5,
    enlarge x limits=false,
    ylabel={Cycle min (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN JKBMS,Growatt CAN SeplosBMS,JKBMS CAN,Pylon CAN,SMA CAN,Sofar CAN,Victron CAN},
    x tick label style={text width=1.3cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,599.849) [599.8] (2,300.246) [300.2] (3,9980.699) [9980.7] (4,251.235) [251.2] (5,9907.993) [9908.0] (6,900.276) [900.3] (7,0.219) [0.2] (8,0.219) [0.2] (9,9960.726) [9960.7]};
\addplot+[fill=forward, draw=forward] coordinates {(3,9980.681) [9980.7] (4,85.691) [85.7]};
\addplot+[fill=direct, draw=direct] coordinates {(3,4980.232) [4980.2] (4,129.933) [129.9]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Minimum CAN cycle duration, log scale.}
\end{subfigure}


\begin{subfigure}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=0.99\textwidth,
    height=5.8cm,
    bar width=7pt,
    ymode=log,
    log basis y=10,
    log origin y=infty,
    ytick={0.1,1,10,100,1000,10000},
    yticklabels={\mbox{10\raisebox{0.55ex}{-1}},\mbox{10\raisebox{0.55ex}{0}},\mbox{10\raisebox{0.55ex}{1}},\mbox{10\raisebox{0.55ex}{2}},\mbox{10\raisebox{0.55ex}{3}},\mbox{10\raisebox{0.55ex}{4}}},
    ymin=0.1,
    ymax=119768,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=9.5,
    enlarge x limits=false,
    ylabel={Cycle max (ms)},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN JKBMS,Growatt CAN SeplosBMS,JKBMS CAN,Pylon CAN,SMA CAN,Sofar CAN,Victron CAN},
    x tick label style={text width=1.3cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,1599.872) [1599.9] (2,7100.062) [7100.1] (3,9980.699) [9980.7] (4,1496.224) [1496.2] (5,9907.993) [9908.0] (6,2299.947) [2299.9] (7,0.237) [0.2] (8,0.237) [0.2] (9,9960.726) [9960.7]};
\addplot+[fill=forward, draw=forward] coordinates {(3,9980.681) [9980.7] (4,871.815) [871.8]};
\addplot+[fill=direct, draw=direct] coordinates {(3,4980.232) [4980.2] (4,831.769) [831.8]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{Maximum CAN cycle duration, log scale.}
\end{subfigure}

\caption{CAN cycle range overview charts.}
\end{figure}



\begin{figure}[p]
\centering

\begin{minipage}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.4cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=11.5,
    enlarge x limits=false,
    ylabel={Complete exchanges/s},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9,10,11},
    xticklabels={China Tower Modbus RS485,Daly RS485,Growatt RS485 JKBMS,Growatt RS485 SeplosBMS,JKBMS Modbus RS485,PACE Modbus RS485,Pylon RS485,Anenji Pylon RS485 JKBMS,Anenji Pylon RS485 SeplosBMS,Voltronic Modbus RS485,WOW Modbus RS485},
    x tick label style={text width=1.05cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,3.900) [3.9] (2,1.760) [1.8] (3,2.500) [2.5] (4,2.400) [2.4] (5,3.900) [3.9] (6,3.900) [3.9] (7,0.360) [0.4] (8,0.800) [0.8] (10,3.900) [3.9] (11,3.900) [3.9]};
\addplot+[fill=forward, draw=forward] coordinates {(3,2.500) [2.5] (4,2.400) [2.4] (8,0.800) [0.8] (9,0.800) [0.8]};
\addplot+[fill=direct, draw=direct] coordinates {(3,2.000) [2.0] (8,0.800) [0.8] (9,0.800) [0.8]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{RS485/UART exchange rate overview chart.}
\end{minipage}

\vspace{0.65cm}

\begin{minipage}{\textwidth}
\centering

\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\textwidth,
    height=4.4cm,
    bar width=7pt,
    ymin=0,
    point meta=explicit symbolic,
    nodes near coords={\pgfplotspointmeta},
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west, inner sep=1pt},
    enlarge y limits={upper,value=0.35},
    clip=false,
    scaled y ticks=false,
    xmin=0.5,
    xmax=9.5,
    enlarge x limits=false,
    ylabel={Cycles/s},
    ylabel style={font=\small},
    xtick={1,2,3,4,5,6,7,8,9},
    xticklabels={Deye CAN,GoodWe CAN,Growatt CAN JKBMS,Growatt CAN SeplosBMS,JKBMS CAN,Pylon CAN,SMA CAN,Sofar CAN,Victron CAN},
    x tick label style={text width=1.3cm, align=center, font=\tiny},
    y tick label style={font=\scriptsize},
    legend style={at={(0.5,1.04)}, anchor=south, legend columns=3, font=\scriptsize},
    grid=both,
    major grid style={draw=gridline},
]
\addplot+[fill=bridge, draw=bridge] coordinates {(1,0.900) [0.9] (2,0.400) [0.4] (3,0.100) [0.1] (4,1.000) [1.0] (5,0.100) [0.1] (6,0.500) [0.5] (7,6.000) [6.0] (8,5.920) [5.9] (9,0.100) [0.1]};
\addplot+[fill=forward, draw=forward] coordinates {(3,0.100) [0.1] (4,1.100) [1.1]};
\addplot+[fill=direct, draw=direct] coordinates {(3,0.200) [0.2] (4,1.200) [1.2]};
\legend{Bridge, Bridge Forward, Direct cable}
\end{axis}
\end{tikzpicture}

\caption{CAN cycle rate overview chart.}
\end{minipage}

\end{figure}


\clearpage


\begin{landscape}

\section{Three-mode Delta Tables}

The following tables focus only on groups where all three modes are available: Bridge, Bridge Forward, and Direct cable. Deltas are directional: orange means an increase, green means a decrease. Timing rows are displayed in milliseconds. Whether an increase is good depends on the metric.

\subsection{RS485/UART Three-mode Deltas}
\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\setlength{\LTpre}{0.35em}
\setlength{\LTpost}{0.45em}
\begin{longtable}{@{}L{5.0cm}L{4.0cm}L{1.65cm}L{1.65cm}L{1.65cm}L{2.8cm}L{2.8cm}L{2.8cm}@{}}
\toprule
Comparison group & Metric & Bridge & Forward & Direct & Forward vs Bridge & Direct vs Bridge & Direct vs Forward \\
\midrule
\endhead
Growatt RS485 JKBMS & Complete exchanges/s & 2.5 & 2.5 & 2 & 0 (0\%) & \decrease{-0.5 (-20\%)} & \decrease{-0.5 (-20\%)} \\
Growatt RS485 JKBMS & Req->Rsp avg (ms) & 4.76 & 5.01 & 5.13 & \increase{+0.25 (+5.2\%)} & \increase{+0.37 (+7.7\%)} & \increase{+0.12 (+2.4\%)} \\
Growatt RS485 JKBMS & Req->Rsp P95 (ms) & 5.29 & 5.29 & 5.44 & 0 (0\%) & \increase{+0.14 (+2.7\%)} & \increase{+0.14 (+2.7\%)} \\
Growatt RS485 JKBMS & Full exchange avg (ms) & 49.09 & 48.93 & 59.34 & \decrease{-0.17 (-0.3\%)} & \increase{+10.24 (+20.9\%)} & \increase{+10.41 (+21.3\%)} \\
Growatt RS485 JKBMS & Full exchange P95 (ms) & 53.52 & 53.48 & 75 & \decrease{-0.04 (-0.1\%)} & \increase{+21.48 (+40.1\%)} & \increase{+21.52 (+40.2\%)} \\
Anenji Pylon RS485 JKBMS & Complete exchanges/s & 0.8 & 0.8 & 0.8 & 0 (0\%) & 0 (0\%) & 0 (0\%) \\
Anenji Pylon RS485 JKBMS & Req->Rsp avg (ms) & 9.71 & 5.49 & 5.12 & \decrease{-4.22 (-43.5\%)} & \decrease{-4.58 (-47.2\%)} & \decrease{-0.36 (-6.6\%)} \\
Anenji Pylon RS485 JKBMS & Req->Rsp P95 (ms) & 9.91 & 6.19 & 5.69 & \decrease{-3.72 (-37.6\%)} & \decrease{-4.22 (-42.6\%)} & \decrease{-0.5 (-8\%)} \\
Anenji Pylon RS485 JKBMS & Full exchange avg (ms) & 111.16 & 106.95 & 102.92 & \decrease{-4.21 (-3.8\%)} & \decrease{-8.25 (-7.4\%)} & \decrease{-4.03 (-3.8\%)} \\
Anenji Pylon RS485 JKBMS & Full exchange P95 (ms) & 153.03 & 149.32 & 145.15 & \decrease{-3.71 (-2.4\%)} & \decrease{-7.88 (-5.1\%)} & \decrease{-4.17 (-2.8\%)} \\
\bottomrule
\end{longtable}
\endgroup





\subsection{CAN Three-mode Deltas}
\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\setlength{\LTpre}{0.35em}
\setlength{\LTpost}{0.45em}
\begin{longtable}{@{}L{5.0cm}L{4.0cm}L{1.65cm}L{1.65cm}L{1.65cm}L{2.8cm}L{2.8cm}L{2.8cm}@{}}
\toprule
Comparison group & Metric & Bridge & Forward & Direct & Forward vs Bridge & Direct vs Bridge & Direct vs Forward \\
\midrule
\endhead
Growatt CAN JKBMS & Frames/s & 51.9 & 52 & 52 & \increase{+0.1 (+0.2\%)} & \increase{+0.1 (+0.2\%)} & 0 (0\%) \\
Growatt CAN JKBMS & Cycles/s & 0.1 & 0.1 & 0.2 & 0 (0\%) & \increase{+0.1 (+100\%)} & \increase{+0.1 (+100\%)} \\
Growatt CAN JKBMS & Cycle min (ms) & 9980.7 & 9980.68 & 4980.23 & \decrease{-0.02 (0\%)} & \decrease{-5000.47 (-50.1\%)} & \decrease{-5000.45 (-50.1\%)} \\
Growatt CAN JKBMS & Cycle avg (ms) & 9980.7 & 9980.68 & 4980.23 & \decrease{-0.02 (0\%)} & \decrease{-5000.47 (-50.1\%)} & \decrease{-5000.45 (-50.1\%)} \\
Growatt CAN JKBMS & Cycle max (ms) & 9980.7 & 9980.68 & 4980.23 & \decrease{-0.02 (0\%)} & \decrease{-5000.47 (-50.1\%)} & \decrease{-5000.45 (-50.1\%)} \\
Growatt CAN JKBMS & Cycle P95 (ms) & 9980.7 & 9980.68 & 4980.23 & \decrease{-0.02 (0\%)} & \decrease{-5000.47 (-50.1\%)} & \decrease{-5000.45 (-50.1\%)} \\
Growatt CAN SeplosBMS & Frames/s & 13 & 12.9 & 13 & \decrease{-0.1 (-0.8\%)} & 0 (0\%) & \increase{+0.1 (+0.8\%)} \\
Growatt CAN SeplosBMS & Cycles/s & 1 & 1.1 & 1.2 & \increase{+0.1 (+10\%)} & \increase{+0.2 (+20\%)} & \increase{+0.1 (+9.1\%)} \\
Growatt CAN SeplosBMS & Cycle min (ms) & 251.23 & 85.69 & 129.93 & \decrease{-165.54 (-65.9\%)} & \decrease{-121.3 (-48.3\%)} & \increase{+44.24 (+51.6\%)} \\
Growatt CAN SeplosBMS & Cycle avg (ms) & 851.37 & 755.94 & 687.13 & \decrease{-95.43 (-11.2\%)} & \decrease{-164.25 (-19.3\%)} & \decrease{-68.82 (-9.1\%)} \\
Growatt CAN SeplosBMS & Cycle max (ms) & 1496.22 & 871.81 & 831.77 & \decrease{-624.41 (-41.7\%)} & \decrease{-664.45 (-44.4\%)} & \decrease{-40.05 (-4.6\%)} \\
Growatt CAN SeplosBMS & Cycle P95 (ms) & 1221.32 & 861.95 & 831.77 & \decrease{-359.37 (-29.4\%)} & \decrease{-389.55 (-31.9\%)} & \decrease{-30.18 (-3.5\%)} \\
Growatt CAN SeplosBMS & Inter-cycle gap min (ms) & 114.67 & 128.17 & 168.23 & \increase{+13.51 (+11.8\%)} & \increase{+53.56 (+46.7\%)} & \increase{+40.05 (+31.2\%)} \\
Growatt CAN SeplosBMS & Inter-cycle gap avg (ms) & 155.49 & 160.23 & 168.23 & \increase{+4.73 (+3\%)} & \increase{+12.74 (+8.2\%)} & \increase{+8 (+5\%)} \\
Growatt CAN SeplosBMS & Inter-cycle gap max (ms) & 165.78 & 165.78 & 168.23 & 0 (0\%) & \increase{+2.45 (+1.5\%)} & \increase{+2.45 (+1.5\%)} \\
Growatt CAN SeplosBMS & Inter-cycle gap P95 (ms) & 165.78 & 165.78 & 168.23 & 0 (0\%) & \increase{+2.45 (+1.5\%)} & \increase{+2.45 (+1.5\%)} \\
\bottomrule
\end{longtable}
\endgroup

\end{landscape}


\clearpage


\begin{landscape}

\section{Capture Overview}

\subsection{RS485/UART Capture Overview}
\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\setlength{\LTpre}{0.35em}
\setlength{\LTpost}{0.45em}
\begin{longtable}{@{}L{4.8cm}L{2.35cm}L{1.4cm}L{1.5cm}L{2.25cm}L{2.25cm}L{2.1cm}@{}}
\toprule
Captured protocol & Topology & Frames & Loss rate & Req->Rsp avg (ms) & Req->Rsp P95 (ms) & Full P95 (ms) \\
\midrule
\endhead
China Tower Modbus RS485 & Bridge & 79 & 2.5\% & 5.02 & 5.34 & 53.53 \\
Daly RS485 & Bridge & 88 & 0\% & 14.46 & 18.06 & 297.65 \\
Growatt RS485 & Bridge & 50 & 0\% & 4.76 & 5.29 & 53.52 \\
Growatt RS485 & Bridge & 49 & 4\% & 49.52 & 49.86 & 97.81 \\
Growatt RS485 & Direct cable & 100 & 0\% & 5.13 & 5.44 & 75 \\
Growatt RS485 & Bridge Forward & 50 & 0\% & 5.01 & 5.29 & 53.48 \\
Growatt RS485 & Bridge Forward & 49 & 4\% & 49.6 & 50.49 & 97.85 \\
JKBMS Modbus RS485 & Bridge & 78 & 0\% & 4.9 & 5.19 & 13.12 \\
PACE Modbus RS485 & Bridge & 79 & 2.5\% & 4.99 & 5.26 & 66.06 \\
Pylon RS485 & Bridge & 49 & 21.74\% & 4.82 & 5.54 & 148.67 \\
Pylon RS485 & Bridge & 20 & 33.33\% & 9.71 & 9.91 & 153.03 \\
Pylon RS485 & Direct cable & 61 & 51.22\% & 5.12 & 5.69 & 145.15 \\
Pylon RS485 & Direct cable & 50 & 33.33\% & 9.89 & 12.04 & 151.5 \\
Pylon RS485 & Bridge Forward & 24 & 50\% & 5.49 & 6.19 & 149.32 \\
Pylon RS485 & Bridge Forward & 20 & 33.33\% & 9.47 & 9.88 & 153 \\
Voltronic Modbus RS485 & Bridge & 78 & 0\% & 99.8 & 101.84 & 119.96 \\
WOW Modbus RS485 & Bridge & 78 & 0\% & 4.8 & 5.09 & 65.81 \\
\bottomrule
\end{longtable}
\endgroup





\subsection{CAN Capture Overview}
\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\setlength{\LTpre}{0.35em}
\setlength{\LTpost}{0.45em}
\begin{longtable}{@{}L{4.8cm}L{2.35cm}L{1.2cm}L{1.0cm}L{1.2cm}L{1.9cm}L{1.9cm}L{1.9cm}L{1.9cm}L{1.1cm}@{}}
\toprule
Captured protocol & Topology & Frames & IDs & Cycles & Cycle min (ms) & Cycle avg (ms) & Cycle max (ms) & Cycle P95 (ms) & Errors \\
\midrule
\endhead
Deye CAN & Bridge & 100 & 8 & 9 & 599.85 & 1011.01 & 1599.87 & 1599.87 & 0 \\
GoodWe CAN & Bridge & 100 & 8 & 4 & 300.25 & 2399.97 & 7100.06 & 6275.02 & 0 \\
Growatt CAN & Bridge & 519 & 10 & 1 & 9980.7 & 9980.7 & 9980.7 & 9980.7 & 0 \\
Growatt CAN & Bridge & 130 & 12 & 10 & 251.23 & 851.37 & 1496.22 & 1221.32 & 0 \\
Growatt CAN & Direct cable & 260 & 10 & 1 & 4980.23 & 4980.23 & 4980.23 & 4980.23 & 0 \\
Growatt CAN & Direct cable & 65 & 12 & 6 & 129.93 & 687.13 & 831.77 & 831.77 & 0 \\
Growatt CAN & Bridge Forward & 520 & 10 & 1 & 9980.68 & 9980.68 & 9980.68 & 9980.68 & 0 \\
Growatt CAN & Bridge Forward & 129 & 12 & 11 & 85.69 & 755.94 & 871.81 & 861.95 & 0 \\
JKBMS CAN & Bridge & 344 & 12 & 1 & 9907.99 & 9907.99 & 9907.99 & 9907.99 & 0 \\
Pylon CAN & Bridge & 100 & 8 & 5 & 900.28 & 1900.01 & 2299.95 & 2299.95 & 0 \\
SMA CAN & Bridge & 60 & 6 & 60 & 0.22 & 0.23 & 0.24 & 0.24 & 0 \\
Sofar CAN & Bridge & 148 & 6 & 148 & 0.22 & 0.23 & 0.24 & 0.24 & 0 \\
Victron CAN & Bridge & 250 & 19 & 1 & 9960.73 & 9960.73 & 9960.73 & 9960.73 & 0 \\
\bottomrule
\end{longtable}
\endgroup

\end{landscape}


\section*{Notes}

\begin{itemize}[leftmargin=*]
\item The LaTeX source is generated from committed CSV files under \texttt{analysis/out/}.
\item Capture durations are not identical, so normalized rates are included where useful.
\item CAN cycle duration can be dominated by capture length when only one cycle is detected.
\item Compiled PDFs and LaTeX build artifacts should stay out of the repository.
\end{itemize}

\end{document}
